---
title: "Assignment"
author: "Scott Stoltzman"
date: "7/15/2019"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library('corrplot') # install.packages('corrplot') --> very handy for correlations of large dataframe
library('mlbench') # install.packages('mlbench')
library("tidyverse")
library('caret')
set.seed(123)

data("PimaIndiansDiabetes") 
```
Data: <https://rdrr.io/cran/mlbench/man/PimaIndiansDiabetes.html>
Data has no `NA` - assume "clean" data for this exercise.

```{r}
dat = PimaIndiansDiabetes %>% 
  as_tibble() %>%
  rename(Class = diabetes) %>%
  mutate(Class = as.factor(Class))
head(dat)
```


# What are we going to try to predict?
Can we predict `pos` or `neg` outcome for diabetes (renamed to `Class`)?

Perform a couple of basic EDA steps.

Start by showing the base rate.
```{r}

```

Visualize the correlation of all variables using the `corrplot.mixed()` function on the `corrplot_dat` data. <https://cran.r-project.org/web/packages/corrplot/vignettes/corrplot-intro.html>
```{r}
corrplot_dat = cor(dat %>% select(-Class))

```

Complete 2 more EDA steps you find interesting
```{r}
# Step 1
```


```{r}
# Step 2
```


Separate out test vs train --> assume training on 75% of data
```{r}

```


Complete any resampling
```{r}

```


Train two types of classification models, describe what the models indicate, and compare results
```{r}

```

